---
title: "Assignment 1: Worley"
subtitle: "BEX5200 Climate Change and Carbon Management Strategies"
author:
- familyname: Faizan
  othernames: Mohammed
  address: Monash University
  email: mfai0014@student.monash.edu
  correspondingauthor: true
  qualifications:  MBAt
department: Our consultancy - Star Wars\newline Mohammed Faizan
organization: Monash University
bibliography: 
- references.bib
- packages.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  bookdown::pdf_document2:
    template: monashreport2.tex
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: true
keep_md: true
always_allow_html: true
---

```{r setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(fig.path = "Figures/", fig.align ="center",
                      out.width = "50%", echo = FALSE, 
                      message = FALSE, 
                      warning = FALSE)
# Loading Libraries
library(tidyverse)
library(readr)
library(kableExtra)
library(tinytex)
library(bookdown)
library(naniar)
library(visdat)
library(citation)
library(knitr)
library(scales)
library(patchwork)
library(sf)
library(glue)
library(unglue)
library(sugarbag)
library(readxl)
library(plotly)
library(tidytext)
library(ggplot2)
library(igraph)
library(ggraph)
```


```{r writing_packages_bibliographies}
knitr::write_bib(c(.packages()), "packages.bib")
```


“Holding the increase in the global average temperature to well below 2°C above pre- industrial levels and pursuing efforts to limit the temperature increase to 1.5°C above pre- industrial levels, recognizing that this would significantly reduce the risks and impacts of climate change” (UNFCCC, 2015, pg. 3).

The forces of change, climate change, the energy transition, the increasing importance of the circular economy, and digitalization of industries have compelled establishments to reform and develop sustainable operations. Energy, oil and gas industries are the sectors where this change is felt more rapidly. Worley, is a leading global provider of professional services headquartered in Australia, delivering project and asset services in the energy, chemicals and resources sectors around the world (@sustainabilityreport2020). This report explores the climate action and sustainable developments made by Worley and the significance of these commitments in the context of climate change, business motives and the risks and opportunities associated with it.




